MLISA: Machine Learning-based \\ Intelligent Service Agents

### 2014-11-05 papers/webservice-coalition-learning/webservice_coalition_learning.tex
changes

In further details, MLISA is applicable for any sort of intelligent agent-based model. To effectively train web services, we used real data set (information about the data set) to extract web services' individual characteristics and used them to measure outcomes when they cooperate with one another. Engineering and extracting these features, we gathered functional and cooperative features for both individual web services and communities in 60 different time slots. We were able to investigate the path a web service might take to achieve the best utility out of effective interaction with others. All paths and the outcomes are labeled to be utilized in training model. Using cross validation set, web services are able to compute optimal hypothesis function (using logistic regression) that can be used to predict outcome out of cooperative work with other individual web services or communities. Our findings show that web services equipped with MLISA have by far better outcome in the form of cooperative service providers than the ones that either do not cooperate or randomly find communities to join.

>>>>

In further details, MLISA is applicable for any sort of intelligent agent-based model. To effectively train web services, we used real data set (information about the data set) to extract web services' individual characteristics and used them to measure outcomes when they cooperate with one another. Engineering and extracting these features, we gathered functional and cooperative features for both individual web services and communities in 64 different time slots. We were able to investigate the path a web service might take to achieve the best utility out of effective interaction with others. All paths and the outcomes are labeled to be utilized in training model. Using cross validation set, web services are able to compute optimal hypothesis function (using logistic regression) that can be used to predict outcome out of cooperative work with other individual web services or communities. Our findings show that web services equipped with MLISA have by far better outcome in the form of cooperative service providers than the ones that either do not cooperate or randomly find communities to join.
